---
title: "p8105_hw1_jl6521"
author: "Jiayi"
date: "2024-09-18"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages("palmerpenguins")
#install.packages("ggplot2")
#install.packages("tidyverse")
library(ggplot2)
library(tidyverse)
```

## Problem 1: dataset description
The penguins dataset contains the 3 species of penguins("species"), name of island ("island") such as Biscoe, Dream, and Torgersen, and their various features, such as their length and depth of bill ("bill_length_mm")("bill_depth_mm"), their flipper length ("flipper_length_mm"), their body mass ("body_mass_g"), their sex ("sex"), and their age ("year"). All the detailed information are listed below in the summary table. The dataset has 344 rows and 8 columns, and the mean flipper length is 200.9152.  
```{r description}
data("penguins", package = "palmerpenguins")
summary(penguins)
nrows = nrow(penguins)
ncols = ncol(penguins)
flipper_length = pull(penguins,flipper_length_mm)
mean_flipper = mean(flipper_length,na.rm = TRUE)
print(paste("The mean flipper length is", mean_flipper))
```

```{r scatterplot}
ggplot(penguins,aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point() + 
  xlab("bill length") + 
  ylab("flipper length") + 
  ggtitle("Scatterplot of flipper length vs bill length") + 
  theme_classic()
ggsave("Scatterplot_flipper_bill_length.jpg", height = 4, width = 6)
```

## Problem 2

The data frame is created: 
```{r problem2}
problem2_df = tibble(
  x = rnorm(10),
  log_vec = c(x>0),
  char_vec = c("Who","is","the","smartest","person","in","the","world","Ya","Ya"),
  fac_vec = factor(c("good","very good","super good","good","very good","super good","good","very good","super good","super good"))
)
problem2_df
```
Next, we found that the numeric random sample and logical vector can take a mean; character vector and factor vector can't take a mean.
```{r}
x = pull(problem2_df, var = x)
mean(x)
log_vec = pull(problem2_df, var = log_vec)
mean(log_vec)
char_vec = pull(problem2_df, var = char_vec)
mean(char_vec)
fac_vec = pull(problem2_df, var = fac_vec)
mean(fac_vec)
```

When we explicitly convert variables from one type to numeric vectors, logical and factor variables are converted successfully to numeric vectors while character variables can't. Logical vectors can be converted to either 0 or 1 since it's only TRUE and FALSE. Factor vectors can be converted to numerical but they are only at their levels. Character variables can't be converted at all.

I think this helps explain the result since the function mean is converting variables to numeric, and logical vectors can be converted. Factor vector can't be converted because the numeric values are only their levels, so calculating the mean is meaningless. Character variables can't be taken mean.  
```{r problem2-2}
new_log = as.numeric(log_vec)
print(new_log)
new_char = as.numeric(char_vec)
new_fac = as.numeric(fac_vec)
print(new_fac)
```

